Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-11-02 paper/amia.tex
Auto Update from local Sharelatex

Ideally a computational investigator should develop, test, and validate models using all available data. This is most easily accomplished when they have unfettered access to all data in the problem domain they are working in. Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand.

@@

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, data scientists or data warehouse owners can insert their own custom method or modify existing methods. Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. For demonstration purposes we have implemented two plugins that use different techniques for data synthesis. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).

>>>>

Ideally a computational investigator should develop, test, and validate models using all available data. This is most easily accomplished when they have unfettered access to all data in the problem domain they are working in. Figure~\ref{fig:architecture} shows the novel architecture of KFP: data access through an intermediary that can synthesize data on-demand. Items in blue are features of KFP; items in grey or with dashed lines are not provided. KFP is designed to fit into an existing infrastructure with a protected data source secured behind a firewall along with user authentication.

@@

Figure~\ref{fig:synthesis_process} shows the automated faux-data request/response process. Items in grey with dashed lines are not provided by KFP but are either pre-existing or provided by the user. All queries submitted to the system are first pre-processed to remove clauses such as "ORDER BY" which are made ineffective by the synthesis process. All queries are logged for later analysis and results cached to optionally improve synthesis performance for repeated queries. Next the processed query is executed against the protected data set and results are passed into the modular synthesis process. While the current implementation only utilizes a couple of synthesis methods, data scientists or data warehouse owners can insert their own custom method or modify existing methods. For additional details on the modular synthesis processes, see the section "Included Synthesis Methods." Previously removed "ORDER BY" clauses are re-applied to the faux-data before results are returned to the user. Finally, although not implemented in this version of KFP, synthetic results could be held back until reviewed and approved for release by the data owner.

@@

KFP provides a framework by which any number of methods for data privacy can be carried out. This framework is comprised of a provided base class, several examples of plugins, and unit tests for validation purposes. As of this writing we have implemented two plugins that use different techniques for data synthesis: a kernel density estimator and DataSynthesizer. The kernel density estimator from scipy.stats.gaussian\_kde uses the method developed by Silverman \cite{silverman_density_1986} which handles inter-related ordinal and ratio data yet runs quickly on standard consumer level hardware. The DataSynthesizer method, created by Ping et al. \cite{ping17datasynthesizer} is built on differential privacy mechanisms and has multiple internal methods for data generation ranging from random generation based on data type to Bayesian modeling of inter-relationships among columns of data. As a result of their methods, the DataSynthesizer offers a unique contribution to the synthetic data generation space: it can work with no configuration other than input data, or can be configured to provide more custom results. In DataSynthesizer, the authors show that the synthetic data generated preserves privacy while still being useful enough for actual data analysis (see also \cite{howe_synthetic_2017}).
